The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-02-09 src/tex/ms.tex
[showyourwork] overleaf sync

\usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{layouts}
% \usepackage{siunitx}

@@

@@

\subsection{Accuracy of astroNN}
\label{sec:astronn-quality}

@@

\subsection{Measurements of the Type Ia Supernova Delay Time Distribution}
\label{sec:dtd-measurements}

\citet{Schonrich2009-RadialMixing} take their DTD to be an exponential with a 1.5 Gyr timescale, though this isn't strictly observationally motivated.

\citet{Maoz2017-CosmicDTD} compare volumetric SN Ia rates to the cosmic star formation history. They get a power law with a slope of $-1.13\pm 0.06$ for field galaxies, and a slope of $-1.39^{+0.32}_{-0.05}$ for galaxy clusters.

\begin{deluxetable}{lCl}
\tablecaption{Sources of the various forms of delay time distribution.}
\tablehead{
\colhead{Name} & \colhead{Form} & \colhead{Source}
}
\startdata
Field Galaxy Power-Law      & t^{-1.1}              & \citet{Maoz2017-CosmicDTD} \\   
Galaxy Cluster Power-Law    & t^{-1.4}              & \citet{Maoz2017-CosmicDTD} \\
Short Exponential           & e^{-t/1.5~\rm{Gyr}}  & \citet{Schonrich2009-RadialMixing} \\
\enddata
\end{deluxetable}

\section{Results}
\label{sec:results}

\subsection{One-Zone Models}
\label{sec:onezone-results}

@@

\subsubsection{The SN Ia Delay-Time Distribution}

@@

\subsubsection{The Minimum SN Ia Delay Time}

@@

\subsubsection{The Star Formation History}

@@

\subsubsection{Analytical Formulations}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/onezone_greggio05_single.pdf}
    \includegraphics{figures/onezone_greggio05_double.pdf}
    \caption{Abundance tracks and distributions from one-zone models with the analytical DTDs from \citet{Greggio2005-AnalyticalRates}. \textit{Left:} a comparison between the analytical SD DTD (solid curve), an exponential DTD with a 1.5 Gyr timescale (dashed curve), and a power-law DTD with a slope of -1.1 (dotted curve). \textit{Right:} a comparison between two different prescriptions for an analytical DD DTD (solid curves), power-law DTDs with an initial plateau of 1 Gyr and 350 Myr (dashed curves), and a power-law DTD with no plateau and a slope of -1.1 (dotted curve).}
    \label{fig:onezone-greggio05}
    \script{onezone_greggio05_single.py}
    \script{onezone_greggio05_double.py}
\end{figure*}

\subsection{Multi-Zone Models}
\label{sec:multizone-results}

>>>>

\usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{layouts}
\usepackage{xcolor}
% \usepackage{siunitx}

@@

% user-defined commands
\newcommand{\yes}{\textcolor{green}{\checkmark}}
\newcommand{\meh}{\textcolor{black}{$\sim$}}
\newcommand{\no}{\textcolor{red}{$\times$}}

@@

\subsection{DTD Models}
\label{sec:dtd-models}

\subsubsection{From Observations}

\citet{Maoz2014-Review}

A typical form for the DTD is a power-law $t^\alpha$ where $\alpha\sim-1$. \citet{Maoz2017-CosmicDTD} compare volumetric SN Ia rates to the cosmic star formation history. They get a power law with a slope of $-1.13\pm 0.06$ for field galaxies, and a slope of $-1.39^{+0.32}_{-0.05}$ for galaxy clusters.

Another commonly assumed functional form is an exponential. \citet{Schonrich2009-RadialMixing} take their DTD to be an exponential with a 1.5 Gyr timescale, though this isn't strictly observationally motivated.

% \begin{deluxetable}{lCl}
% \tablecaption{Sources of the various forms of delay time distribution.}
% \tablehead{
% \colhead{Name} & \colhead{Form} & \colhead{Source}
% }
% \startdata
% Field Galaxy Power-Law      & t^{-1.1}              & \citet{Maoz2017-CosmicDTD} \\   
% Galaxy Cluster Power-Law    & t^{-1.4}              & \citet{Maoz2017-CosmicDTD} \\
% Short Exponential           & e^{-t/1.5~\rm{Gyr}}  & \citet{Schonrich2009-RadialMixing} \\
% \enddata
% \end{deluxetable}

\subsubsection{Theoretical Models}

\citet{Matteucci1986-SupernovaEnrichment}

\citet{Greggio2005-AnalyticalRates}

\citet{Rajamuthukumar2022-TripleEvolution}

\citet{Schonrich2009-RadialMixing,Weinberg2017-ChemicalEquilibrium} assume an exponential with $\tau=1.5$ Gyr

\begin{figure}
    \centering
    \includegraphics{figures/dtd_greggio05.pdf}
    \caption{Analytical DTDs from \citet[][solid curves]{Greggio2005-AnalyticalRates} and close approximation simple functions (dashed curves).}
    \label{fig:dtd-greggio05}
\end{figure}

\subsubsection{Our Models}

We explore four different classes of DTD: a power-law, a broken power-law with an initial flat plateau, an exponential, and an exponential with a prompt Gaussian component, with one or two different parameterizations for each. Figure \ref{fig:dtds} presents these DTDs as a function of time since star formation.

The power-law DTD is motivated by studies of the cosmic Ia rate \citep{Maoz2017-CosmicDTD,Wiseman2021-DESRates}, and we explore slopes of $\alpha=-1.1$ and $\alpha=-1.4$ which correspond to the field galaxy and galaxy cluster DTDs of \citet{Maoz2017-CosmicDTD}, respectively. We explore the broken power-law with plateau widths of 300 Myr and 1 Gyr \textemdash the first as a proxy for both

\subsection{APOGEE Data}
\label{sec:apogee-data}

\subsubsection{Accuracy of astroNN}
\label{sec:astronn-quality}

@@

\subsection{Chemical Evolution Models}
\label{sec:vice-models}

\section{Results from Single-Zone Models}
\label{sec:onezone-results}

@@

\subsection{The SN Ia Delay-Time Distribution}

@@

\subsection{The Minimum SN Ia Delay Time}

@@

\subsection{The Star Formation History}

@@

\subsection{Analytical Formulations}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/onezone_greggio05_single.pdf}
    \includegraphics{figures/onezone_greggio05_double.pdf}
    \caption{Abundance tracks and distributions from one-zone models with the analytical DTDs from \citet{Greggio2005-AnalyticalRates}. \textit{Left:} a comparison between the analytical SD DTD (solid curve), an exponential DTD with a 1.5 Gyr timescale (dashed curve), and a power-law DTD with a slope of -1.1 (dotted curve). \textit{Right:} a comparison between two different prescriptions for an analytical DD DTD (solid curves), power-law DTDs with an initial plateau of 1 Gyr and 350 Myr (dashed curves), and a power-law DTD with no plateau and a slope of -1.1 (dotted curve).}
    \label{fig:onezone-greggio05}
    \script{onezone_greggio05.py}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics{figures/onezone_prompt.pdf}
    \caption{Caption}
    \label{fig:onezone-prompt}
    \script{onezone_prompt.py}
\end{figure}

\section{Results from Multi-Zone Models}
\label{sec:multizone-results}

\section{Discussion}
\label{sec:discussion}

Picking the team.

\begin{deluxetable*}{ll|cccc}
\label{tab:results}
\tablehead{
\colhead{DTD} & \colhead{SFH} & \colhead{MDF} & \colhead{ODF} & \colhead{[Fe/H]--[O/Fe]} & \colhead{Age--[O/Fe]}
}
\startdata
Power law               & Inside-out    & \meh  & \no   & \meh  & \no     \\
($\alpha=-1.1$)         & Late burst    & \meh  & \no   & \meh  & \no     \\
                        & Early burst   & \no   & \yes  & \meh  & \meh    \\
                        & Two-infall    & \no   & \no   & \meh  & \no     \\
\hline
Power law               & Inside-out    & \meh  & \no   & \no   & \no     \\
($\alpha=-1.4$)         & Late burst    & \meh  & \no   & \no   & \no     \\
                        & Early burst   & \no   & \yes  & \no   & \meh    \\
                        & Two-infall    & \no   & \no   & \no   & \no     \\
\hline
Exponential             & Inside-out    & \yes  & \no   & \yes  & \no     \\
($\tau=1.5$ Gyr)        & Late burst    & \yes  & \no   & \yes  & \no     \\
                        & Early burst   & \no   & \yes  & \meh  & \yes    \\
                        & Two-infall    & \yes  & \meh  & \meh  & \meh    \\
\hline
Exponential             & Inside-out    & \yes  & \meh  & \yes  & \meh    \\
($\tau=3$ Gyr)          & Late burst    & \yes  & \meh  & \yes  & \meh    \\
                        & Early burst   & \no   & \yes  & \no   & \yes    \\
                        & Two-infall    & \meh  & \meh  & \meh  & \meh    \\
\hline
Plateau                 & Inside-out    & \yes  & \meh  & \yes  & \no     \\
($W=0.3$ Gyr)           & Late burst    & \yes  & \no   & \yes  & \no     \\
                        & Early burst   & \no   & \yes  & \meh  & \yes    \\
                        & Two-infall    & \yes  & \meh  & \yes  & \meh    \\
\hline
Plateau                 & Inside-out    & \meh  & \meh  & \yes  & \meh    \\
($W=1.0$ Gyr)           & Late burst    & \meh  & \meh  & \yes  & \meh    \\
                        & Early burst   & \no   & \yes  & \no   & \yes    \\
                        & Two-infall    & \meh  & \meh  & \meh  & \meh    \\
\hline
Prompt                  & Inside-out    & \meh  & \no   & \no   & \no     \\
($t_{50}=0.1$ Gyr)      & Late burst    & \meh  & \no   & \no   & \no     \\
                        & Early burst   & \no   & \yes  & \no   & \yes    \\
                        & Two-infall    & \yes  & \no   & \no   & \no     \\
\hline
Triple system           & Inside-out    & \yes  & \meh  & \meh  & \yes    \\
($t_{\rm{max}}=1$ Gyr)  & Late burst    & \yes  & \yes  & \meh  & \meh    \\
                        & Early burst   & \no   & \meh  & \no   & \yes    \\
                        & Two-infall    & \meh  & \meh  & \meh  & \meh    \\
\enddata
\end{deluxetable*}

\section{Conclusions}
\label{sec:conclusions}

\appendix
